---
title: "Vishal Katti"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(tidyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(googlesheets4)
library(gt)
```


```{r gsheet, message=FALSE, warning=FALSE, comment=""}
gsheet <- "1W9duSTZ9hAhlV3yxFeM7qqIFc8Gca2utVe4WxMg0_1A"
gs4_auth(email = "katti.vishal@gmail.com")

skills         <- read_sheet(ss = gsheet, sheet = "Skills")
tools          <- read_sheet(ss = gsheet, sheet = "Tools")
highlights     <- read_sheet(ss = gsheet, sheet = "Highlights")
certifications <- read_sheet(ss = gsheet, sheet = "Certifications")
work           <- read_sheet(ss = gsheet, sheet = "Work")
education      <- read_sheet(ss = gsheet, sheet = "Education")

```

### Hi there 👋

[![Twitter Badge](https://img.shields.io/badge/-Twitter-1ca0f1?style=flat-square&labelColor=1ca0f1&logo=twitter&logoColor=white&link=https://twitter.com/vishal_katti)](https://twitter.com/vishal_katti)

- 🔭 I’m currently working on building my personal Github profile. My work org. started using Github a few months ago for work-related collaboration, where I have moved all my R/Python automation scripts online. I have also developed a few internal R packages which are extensively used within my team.
- 🌱 I’m currently learning Statistics with R from Coursera offered by Duke University. I am also learning to manage my productivity in this pandemic-induced work-from-home period.
- 👯 I’m looking to collaborate on anything R related outside of my work network.
- 🤔 I’m looking for career guidance.
- 💬 Ask me about how R can help automate your Excel reports.
- 📫 How to reach me: twitter
- ⚡ Fun fact: The data in this .md file comes from Google Sheets and is created with R and 💖

## Work Experience




```{r work}
exp_months <- as.period(Sys.Date() - as_date("2010-09-28")) %/% months(1)

exp_mon <- exp_months %% 12
exp_yrs <- exp_months %/% 12

work %>% 
  mutate(
    From = lubridate::as_date(From),
    To = lubridate::as_date(To)
    ) %>% 
  group_by(Employer) %>% 
gt() %>%
  tab_header(title = glue::glue(" Total {exp_yrs} Years {exp_mon} Months Experience.")) %>% 
  tab_source_note(md("Data Source: Vishal's MyCV GSheet. Built with {gt}")) %>%
  cols_label(Loc = "Location", Position = "Role",From = "From", To = "To") %>% 
  tab_style(style = cell_text(weight = "bold"), locations = cells_body(rows = 1:2)) %>% 
  tab_style(style = cell_text(color = "gray"), locations = cells_body(rows = 3:7)) %>% 
  fmt(columns = 4:5, fns = function(x) ifelse(!is.na(x), format(x, '%b %Y'),"Till Date")) %>% 
  tab_options(table.font.size = 12, 
              column_labels.font.weight = "bold", 
              data_row.padding = px(1), 
              table.align = "left",
              source_notes.font.size = 9,
              row_group.background.color = "#4169E1",
              row_group.font.size = 14,
              row_group.font.weight = "bold"
              )
```

```{r}
work %>% 
  mutate(
    From = format(lubridate::as_date(From),"%b %Y"),
    To = if_else(is.na(To), "Till Date",format(lubridate::as_date(To), "%b %Y"))
    ) %>% 
  setNames(c("Employer","Location","Role","From","To")) %>% 
  knitr::kable(caption = glue::glue(" Total {exp_yrs} Years {exp_mon} Months Experience."))
```


## Career Highlights

```{r highlights}
highlights %>% 
  mutate(Start = format(Start, "%b %Y"),
         End = format(End, "%b %Y"),
         When = if_else(is.na(End), Start, paste0(Start, "-", End))) %>% 
  select(-c(Start, End)) %>% 
  gt() %>% 
  tab_source_note("Data Source: Vishal's MyCV GSheet. Built with {gt}") %>% 
  tab_options(table.font.size = 12, 
              column_labels.font.weight = "bold", 
              data_row.padding = px(1), 
              table.align = "left",
              source_notes.font.size = 9)
```

## Skills

```{r skills}
gt(skills) %>% 
  tab_source_note("Data Source: Vishal's MyCV GSheet. Built with {gt}") %>% 
  tab_options(table.font.size = 12, 
              column_labels.font.weight = "bold", 
              data_row.padding = px(1), 
              table.align = "left",
              source_notes.font.size = 9)
```

```{r tools}
tools %>% mutate(Tool = factor(Tool, levels = c("MS Access", "Python", "SQL", "MS Visio", "MS Word", "MS Powerpoint", "MS Excel", "VBA", "R"))) %>% 
ggplot() +
  theme_minimal() +
  geom_col(aes(x = Score, y = Tool, fill = Score)) +
  geom_text(aes(x = 0.25, y = Tool, label = Tool), hjust = 0, color = "white") +
  geom_text(aes(x = Score-0.25, y = Tool, label = paste0(Score,"/10")), hjust = 1, color = "white") +
  expand_limits(x = c(0, 10), y = c(0,0)) +
  scale_fill_gradient2() +
  ggtitle("Tool Competency Levels", 
       subtitle = "Scores out of 10 for each tool.") +
  labs(caption = "Data Source: Vishal's MyCV GSheet. Built with {ggplot2}") +
  theme(legend.position = "none",
        axis.title = element_blank(),
        axis.text = element_blank(),
        panel.grid = element_blank(),
        plot.caption = element_text(hjust = 0)
        )
```

## Education

```{r education}
gt(education) %>% 
  tab_source_note("Data Source: Vishal's MyCV GSheet. Built with {gt}") %>% 
  fmt(columns = vars(From, To), fns = function(x) format(x, "%b %Y")) %>% 
  tab_options(table.font.size = 12, 
              column_labels.font.weight = "bold", 
              data_row.padding = px(1), 
              table.align = "left",
              source_notes.font.size = 9)
```












